Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2019-12-08 fertile.Rmd
more edits (still need final section)

In defining the steps toward creating reproducible analyses, researchers place their emphasis on different areas, including file structure, documentation, the use of file paths in code, and accessibility. Within these categories, the recommendations for what steps to take in ensuring reproducibility also vary.

Much of the discussion around reproducibility is also generalized, written in a way applicable to users working with a variety of statistical software programs. As a result, analysts interested in practicing reproducibility cannot easily access recommendations tailored specifically to their programming language or software of choice.

Additionally, all statistical software programs operate differently. Since analysts do not all share the same software preferences, there can be no single set of recommendations or guidelines for reproducibility. Instead, recommendations must be specific to certain software programs.

In this paper, we focus on reproducibility in the R programming language, with a specific concentration on the RStudio integrated development environment, due to its popularity for statistical analyses and the ease with which analysts can download and begin using the software.

>>>>

In defining the steps toward creating reproducible analyses, different researchers place their emphasis on different areas, including file structure, documentation, the use of file paths in code, and accessibility. Within these categories, the recommendations for what steps to take in ensuring reproducibility also vary.

Much of the discussion around reproducibility is also generalized, written in a way applicable to users working with a variety of statistical software programs. Since all statistical software programs operate differently, generalized recommendations on reproducibility often cannot go in depth. While they provide some useful guidelines, they can often be relatively unhelpful, particularly to new analysts who are unsure how to apply such recommendations within the software programs they are using.

In order to be most effective, reproducibility recommendations must be tailored to specific software programs. However, there has been very little work on reproducibility that is tailored to this level of specificity. In this paper, attempt to remedy that, focusing on reproducibility in the R programming language with a concentration on the RStudio integrated development environment.

R is an ideal candidate for reproducibility recommendations due to the language's popularity for statistical analyses and the ease with which analysts can download and begin using the software.
